Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-02 main.Rmd
added Nick in acknowledgement
aperiodic picture and caption update

```{r aperiodic-example, echo=FALSE,out.width = "100%",fig.cap="The time domain distributed as linear aperiodic granularities $M1$, $M2$, $M$ and aperiodic cyclic granularity $A(B, M)$ relating them with bottom granularity $B$. $A(B, M)$ have repeating patterns with three categories, two of which correspond to the aperiodic linear granularities $M1$ and $M2$ and other one correponding to no aperiodic granularity."}
knitr::include_graphics("Figs/aperiodic-ex.png")
```

@@

The authors would like to thank the cohort at [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team), Monash University for sharing their wisdom and experience of developing R packages, Dr. Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs on improving the analysis of smart meter application. The package `gravitas` was built under [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). More details about the package 
can be found on the package website https://sayani07.github.io/gravitas/. This article was created with knitr [@knitr, @R-knitr] and R Markdown [@rmarkdown, @R-rmarkdown]. The project's Github repository <https://github.com/Sayani07/paper-gravitas> contains all materials required to reproduce this article and the code is also available online
in the supplemental materials.

>>>>

```{r aperiodic-example, echo=FALSE,out.width = "100%",fig.cap="Terminology and intuition of aperiodic cyclic granularities are shown. Panel a shows the time domain distributed as linear granularities Day, Semester, Semester Week, within semester breaks, in-session and aperiodic cyclic granularity Week-of-semester. $A(B, M)$ consists of three categories, 1, 2 and 0 corresponding to within semester breaks, in-session and non-semester period respectively. Panel b depicts the intuition through a measuring tape analogy which needs to be folded at different points every year since $M1$ and $M2$ will fall in different weeks."}
knitr::include_graphics("Figs/aperiodic-ex2.png")
```

@@

The authors would like to thank the cohort at [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team), Monash University for sharing their wisdom and experience of developing R packages, Dr. Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs on improving the analysis of smart meter application. The package `gravitas` was built under [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). We would also like to thank Nicholas Spyrison for many useful discussions and feedback on the manuscipt. More details about the package 
can be found on the package website https://sayani07.github.io/gravitas/. This article was created with knitr [@knitr, @R-knitr] and R Markdown [@rmarkdown, @R-rmarkdown]. The project's Github repository <https://github.com/Sayani07/paper-gravitas> contains all materials required to reproduce this article and the code is also available online
in the supplemental materials.
